Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-09-25 paper/meg_exps.tex
moved figure with vspace

The corresponding results can be found in Figure \ref{fig:meg_results}.

\begin{wrapfigure}{r}{.5\textwidth}
  \begin{center}
    \includegraphics[width=0.48\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg.pdf}

    \label{fig:meg_results}
  \end{center}
  \caption{Multiple models (color-coded) are compared on their ability to reliably predict single-trial MEG signals evoked by words. Left. Average improvement of correlation coefficient $\Delta R$ for each pf the four features (rows). Error bars indicate standard error of the mean (SEM) across subjects. Right. Average $\Delta R$ across time for each subject (dot). Top horizontal lines indicate when B2B significantly outperform other methods.}
\end{wrapfigure}

@@

Word Length and Word Frequency improved the prediction performance of all methods: $\Delta R>0$ for all models (all $p<0.0001$). As expected, the time course associated with Word Length and Word Frequency rose from $\approx$ 100 ms and from $\approx$ 400 ms respectively. Furthermore, Word Function improved the prediction performance of all models (all $p < 0.0002$) except PLS ($p=0.7989$). Overall, these results confirm that Word Length, Word Frequency and Word Function causally influence specific periods of brain responses to words.

>>>>

Corresponding results are shown in Figure~\ref{fig:meg_results}.

\begin{wrapfigure}{r}{.5\textwidth}
  \vspace{-12ex}
  \begin{center}
    \includegraphics[width=0.48\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg.pdf}

    \label{fig:meg_results}
  \end{center}
  \caption{Multiple models (color-coded) are compared on their ability to reliably predict single-trial MEG signals evoked by words. Left. Average improvement of correlation coefficient $\Delta R$ for each pf the four features (rows). Error bars indicate standard error of the mean (SEM) across subjects. Right. Average $\Delta R$ across time for each subject (dot). Top horizontal lines indicate when B2B significantly outperform other methods.}
  \vspace{-9ex}
\end{wrapfigure}

@@

Word Length and Word Frequency improved the prediction performance of all methods: $\Delta R>0$ for all models (all $p<0.0001$). As expected, the time course associated with Word Length and Word Frequency rose from $\approx$ 100 ms and from $\approx$ 400 ms respectively. Furthermore, Word Function improved the prediction performance of all models (all $p < 0.0002$) except for PLS~($p=0.7989$). Overall, these results confirm that Word Length, Word Frequency and Word Function causally influence specific periods of brain responses to words.
